\documentclass{book}

% PACKAGES
%--------------------------------------------------------------------------%
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{wrapfig}

\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{epigraph}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{adjustbox}

\DeclareMathOperator*{\argmin}{arg\,min} %argmin
\DeclareMathOperator*{\argmax}{arg\,max} %argmax

\usepackage{floatrow}
% Table float box with bottom caption, box width adjusted to content
\newfloatcommand{capbtabbox}{table}[][\FBwidth]
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}

%%%

\usepackage{array}
% For tabulars
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}


\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{longtable}
%\usepackage[export]{adjustbox}
%\usepackage{tabu}
\usepackage{xcolor,colortbl}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{amsfonts}

% LOAD CUSTOM COMMANDS FROM A FILE
%--------------------------------------------------------------------------%
%\usepackage{result_figures}


% TITLE
%--------------------------------------------------------------------------%

\title{
    {\bf Geometrical Modeling} \\ Interface for Virtual Space interaction    \vspace{50pt} {\bf Modelowanie Geometryczne} Uniwersalny Interface do interakcji w przestrzenie wirtualnej
}
\author{Jakub Ciecierski}
\date{\today}



% DOCUMENT
%--------------------------------------------------------------------------%

\begin{document}


\begin{titlepage}
    \begin{center}

            \textbf{\huge  Geometrical Modeling.} \\ {\huge Interface for Virtual Space interaction.} \\ [0.5cm]
            
            \textbf{\huge  Modelowanie Geometryczne.} \\ {\huge Uniwersalny Interface do interakcji w przestrzenie wirtualnej.} \\ [0.5cm]
            
            \vspace*{\fill}

            \textbf{\large Jakub Ciecierski}

            \vspace*{\fill}
            
            \textnormal{\large Warsaw University of Technology \\ Factulty of Mathematics and Information Science. \\ \today}

    \end{center}
\end{titlepage}

\tableofcontents









\chapter*{Introduction}

\chapter{Projects}

\section{Project 1}
{\bf Dates} 25.02.2016 - 03.03.2016 (1 week)

Requirements
\begin{enumerate}
    \item Translation, Scaling and Rotating of entire scene.
    \item Affine coordinates. Save all affine transformations as one combined matrix $M \in R^4 \times R^4$.
    \item Net model of Torus. Vertices and edges must be carefully prepared. Edges must point to vertices, and must remain topology independently of drawing order.
    \item The net density dynamically changeable.
\end{enumerate}

%---------------------------------------------------------------
\begin{thebibliography}{1}
    
    
\end{thebibliography}


\end{document}
